---
title: "Plots of $f(x)$"
author: "Daniel Winkler"
date: "September 26, 2016"
output: 
  html_document: 
    toc: true
    fig_height: 3
    fig_width: 8
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Intro
This document shows the graphs of a few functions as well as tables of corresponding values of some of those functions. Feel free to add graphs, comments, tables or whatever else you find interesting in this context. It is written in english in order to be readable for  as many people as possible. Feel free to translate to a language of your choice!


## Plot of $x^n$ for $n = [2,7]$
```{r, echo = FALSE, warning=FALSE}
library(knitr)
library(ggplot2)
ggplot(data.frame(x=c(-10,10)), aes(x))+ ylim(-50,50)+
  stat_function(fun=function(x)x^2, geom='line', aes(color = 'x^2'))+
  stat_function(fun=function(x)x^3, geom='line', aes(color = 'x^3'))+
  stat_function(fun=function(x)x^4, geom='line', aes(color = 'x^4'))+
  stat_function(fun=function(x)x^5, geom='line', aes(color = 'x^5'))+
  stat_function(fun=function(x)x^6, geom='line', aes(color = 'x^6'))+
  stat_function(fun=function(x)x^7, geom='line', aes(color = 'x^7'))+
  coord_cartesian(ylim = c(-25,25), xlim = c(-3,3))

## Only even

ggplot(data.frame(x=c(-10,10)), aes(x))+ ylim(-30,30)+
  stat_function(fun=function(x)x^2, geom='line', aes(color = 'x^2'))+
  stat_function(fun=function(x)x^2/2, geom='line', aes(color = 'x^2/2'))+
  stat_function(fun=function(x)x^4, geom='line', aes(color = 'x^4'))+
  #stat_function(fun=function(x)x^5, geom='line', aes(color = 'x^5'))+
  stat_function(fun=function(x)x^6, geom='line', aes(color = 'x^6'))+
  #stat_function(fun=function(x)x^7, geom='line', aes(color = 'x^7'))+
  coord_cartesian(ylim = c(0,4), xlim = c(-2,2))

## Only odd

ggplot(data.frame(x=c(-10,10)), aes(x))+ ylim(-30,30)+
 # stat_function(fun=function(x)x^2, geom='line', aes(color = 'x^2'))+
  stat_function(fun=function(x)x^3, geom='line', aes(color = 'x^3'))+
 # stat_function(fun=function(x)x^4, geom='line', aes(color = 'x^4'))+
  stat_function(fun=function(x)x^5, geom='line', aes(color = 'x^5'))+
 # stat_function(fun=function(x)x^6, geom='line', aes(color = 'x^6'))+
  stat_function(fun=function(x)x^7, geom='line', aes(color = 'x^7'))+
  coord_cartesian(ylim = c(-10,10), xlim = c(-2,2))

vals <- seq(-3,3, by = 0.5)
table3 <- vector()
for (x in vals){
  y <- x^3
  xy <- cbind(x, y)
  table3 <- rbind(table3, xy)
}
colnames(table3)<-c('x','x^3')
table5 <- vector()
for (x in vals){
  y <- x^5
  xy <- cbind(x,y)
  table5 <- rbind(table5, xy)
}
colnames(table5)<-c('x','x^5')
table3_5<-merge(table3, table5)
table7 <- vector()
for (x in vals){
  y <- x^7
  xy <- cbind(x,y)
  table7 <- rbind(table7, xy)
}
colnames(table7)<-c('x','x^7')
table_odd <- merge(table3_5, table7)


table2 <- vector()
for (x in vals){
  y <- x^2
  xy <- cbind(x, y)
  table2 <- rbind(table2, xy)
}
colnames(table2)<-c('x','x^2')
table4 <- vector()
for (x in vals){
  y <- x^4
  xy <- cbind(x,y)
  table4 <- rbind(table4, xy)
}
colnames(table4)<-c('x','x^4')
table2_4<-merge(table2, table4)
table6 <- vector()
for (x in vals){
  y <- x^6
  xy <- cbind(x,y)
  table6 <- rbind(table6, xy)
}
colnames(table6)<-c('x','x^6')

table_even <- merge(table2_4, table6)
table_all <- merge(table_even, table_odd)
kable(table_all, digits = 5, caption = '$x^n$')
```

## Plot of $\frac{x}{x^2-n}$ for $n=[1,3]$
```{r, echo = FALSE}
eq <-function(x) ifelse(x == 1 | x == -1,NA, (x/((x^2)-1)))
eq2 <-function(x) ifelse(x == sqrt(2) | x == -sqrt(2), NA, (x/((x^2)-2)))
eq3 <-function(x) ifelse(x == sqrt(3) | x == -sqrt(3), NA,(x/((x^2)-3)))

ggplot(data.frame(x=c(-5,5)), aes(x))+
  stat_function(fun=function(x)x/x^2, aes(color = 'x/x^2'))+
  stat_function(fun=eq,geom="line", aes(color="x/(x^2-1)"))+
  stat_function(fun=eq2,geom='line',aes(color='x/(x^2-2)')) +
  stat_function(fun=eq3,geom='line', aes(color ='x/(x^2-3)'))+
  scale_x_continuous(breaks = (seq(-3, 3, by = 1)))+ 
  ylim(-10,10)+
  coord_cartesian(ylim=c(-3,3), xlim=c(-3,3))
  
# Table of Values for x/((x^2)-1)

table_l<-vector()
for(x in seq(-3,-1, 0.1)){
  y<-x/((x^2)-1)
  xy <- cbind(x,y)
  table_l <- rbind(table_l,xy)
}
colnames(table_l)<-c('x','Left part')

table_m<-vector()
for(x in seq(-1,1, 0.1)){
  y<-x/((x^2)-1)
  xy <- cbind(x,y)
  table_m <- rbind(table_m,xy)
}
colnames(table_m)<-c('x','Middle part')

table_r<-vector()
for(x in seq(1,3, 0.1)){
  y<-x/((x^2)-1)
  xy <- cbind(x,y)
  table_r <- rbind(table_r,xy)
}
colnames(table_r)<-c('x','Right part')
table_lmr <-cbind(table_l, table_m, table_r)

kable(table_lmr, caption = '$\\frac{x}{x^2-1}$')
```

## Plot of $ln(x)$ and $\frac{1}{ln(x)}$
```{r, echo = FALSE, warning=FALSE}
ggplot(data.frame(x=c(0,6)), aes(x))+
  stat_function(fun=function(x)1/log(x), aes(color = '1/ln(x)'))+
  stat_function(fun=function(x)log(x), aes(color = 'ln(x)'))+
   scale_x_continuous(breaks = (seq(0, 5, by = 1)))+ 
  ylim(-19,18)+
  coord_cartesian(ylim=c(-9,9), xlim=c(0,5))
```

## Proposed to add

1. $sin(x)$
    + $\frac{1}{sin(x)}$
    + $sin(x^2)$
2. $cos(x)$
## Changelog
1. Document created
